---
title: "Vignette Title"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r}
library(magrittr)
library(satchel)
```

Satchels are specified to a particular root directory, conventionally called `satchel`.

For a project, a directory can be initialized using
`init_satchel_dir()` into data/derived/satchel (Default), or a custom
directory can also be specified

```{r}
init_satchel_dir("satchel")
```

A satchel can be initialized, which will store data in a namespace,
such that multiple satchels can be created to store objects with the 
same name.

```{r}
satchel <- Satchel$new("example_namespace", "./satchel")
```

Objects are saved to satchel via `save()`
```{r}
small_theoph <- head(Theoph)
satchel$save(small_theoph)
```

and queried via `available()`

```{r}
satchel$available()
```

```{r}
new_theoph <- satchel$use("small_theoph")
```

```{r}
all.equal(small_theoph, new_theoph)
```



